---
title: "Viridis Color Palettes"
author: "Posit Connect Cloud"
date: "`r Sys.Date()`"
output:
  html_document: default
---

```{r setup, include = FALSE}
# Set global knit options (optional)
knitr::opts_chunk$set(echo = FALSE)

# load packages
library(tidyverse)
library(viridis)
library(here)
library(maps)
library(sf)

# load data and functions
source("plot_temps.R")
```

## Viridis

The [viridis](https://sjmgarnier.github.io/viridis/) package provides eight eye-catching color palettes to use in data visualizations.

## Optimized for perception

According to the virids documentation, the palettes:

> are designed to improve graph readability for readers with common forms of color blindness and/or color vision deficiency. The color maps are also perceptually-uniform, both in regular form and also when converted to black-and-white for printing.

## Viridis in action

Each plot uses a different viridis color palette to visualize the median high temperature (F) by US county.

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("magma")
plot_temps("inferno")
```

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("plasma")
plot_temps("viridis")
```

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("cividis")
plot_temps("rocket")
```

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("mako")
plot_temps("turbo")
```

## Usage

To use a viridis palette in your plot, include `scale_*_viridis()` in your ggplot2 call:

```{r eval = FALSE, echo = TRUE}
mpg |>  
  ggplot(aes(x = displ, y = cty, color = hwy)) +
    geom_point() +
    scale_color_viridis(option = "A")
```
